Instructions for Authors

### 2014-03-06 paper/appendix.tex
add figures and tables

>>>>

\subsection{Expectation of an individual likelihood term}
The expectation of an individual likelihood term with respect to the posterior distribution is given by:
\begin{align}
\nonumber
l_{in} =& \int \log p(y_{in} | \g_n, h_{in}) \prod_{j=1}^Q p(g_{jn} | \u_j) p(h_{in} | \u_i) \der \g_n \der h_{in} \\
\nonumber
=& \log \Normal(y_{in}; \sum_{j=1}^Q w_{ij} \mu_{jn}+ \mu^h_{in}, \beta_i^{-1}) \\
&- \frac{1}{2} \beta_i \sum_{j=1}^Q w_{ij}^2 \tilde{k}_{nn} 
- \frac{1}{2} \beta_i \tilde{k}^h_{inn},
\label{eq:lin}
\end{align}
where $\tilde{k}_{nn} = (\tilde{\K})_{nn}, \tilde{k}^h_{inn} = (\tilde{\K}^h_i)_{nn}, \mu_{jn} = (\Mu_j)_n, \text{ and } \mu^h_{in} = (\Mu^h_i)_n$.

% previous detailed derivation
%\begin{align}
%\nonumber
%l_{in} &= \int \log p(y_{in} | g_n, h_{in}) p(\g | \ug) p(\h_i | \u_i) \der \g \der \h_i \\
%\nonumber
%&= \int \log \Normal(y_{in} ; w_i g_n + h_{in}, \beta_i^{-1}) 
%\Normal(g_n ; \mu_{gn}, \tilde{k}_{gnn})
%\Normal(h_{in} ; \mu_{in}, (\tilde{k}_{inn}) \der g_n \der h_{in} \\
%\nonumber
%&= -\frac{1}{2} \log 2 \pi \beta_i^{-1} - \frac{1}{2} \int (y_{in} - w_i g_n - h_{in}) \beta_i (y_{in} - w_i g_n - h_{in})
%\Normal(g_n ; \mu_{gn}, \tilde{k}_{gnn})
%\Normal(h_{in} ; \mu_{in}, \tilde{k}_{inn}) \der g_n \der h_{in} \\
%\nonumber
%&= -\frac{1}{2} \log 2 \pi \beta_i^{-1} - \frac{1}{2} \int \left[(y_{in} - h_{in} - w_i \mu_{gn}) \beta_i (y_{in} - h_{in} - w_i \mu_{gn}) + w_i^2 \beta_i \tilde{k}_{gnn} \right] 
%\Normal(h_{in} ; \mu_{in}, \tilde{k}_{inn}) \der h_{in} \\
%\nonumber
%&= -\frac{1}{2} \log 2 \pi \beta_i^{-1} - \frac{1}{2} w_i^2 \beta_i \tilde{k}_{gnn}
%- \frac{1}{2} \beta_i \tilde{k}_{inn} - \frac{1}{2} (y_{in} - w_i \mu_{gn} - \mu_{in}) \beta_i (y_{in} - w_i \mu_{gn} - \mu_{in}) \\
%&= \log \Normal(y_{in}; w_i \mu_{gn} + \mu_{in}, \beta_i^{-1})  - \frac{1}{2} \beta_i (w_i^2 \tilde{k}_{gnn} + \tilde{k}_{inn}),
%\end{align}

### 2014-03-06 paper/experiments.tex
add figures and tables

\subsection{TOY PROBLEM}
In this toy problem we use two related outputs generated from the same latent function $sin(x)$ but are corrupted by independent noises: $y_1(x) = sin(x) + \epsilon$ and $y_2(x) = -sin(x) + \epsilon$, $\epsilon \sim \Normal(0,0.01)$.
Each output has missing values in one region of the input space.
% Say that this is from a single gpsvi
The predictive distributions of the model compared to that of independent gps are shown in \ref{fig5}.

\begin{figure*}
\centering
\begin{tabular}{cc}
\includegraphics[scale=0.5]{figures/ssvi2-y1.eps} &
\includegraphics[scale=0.5]{figures/ssvi2-svi1.eps} \\
\includegraphics[scale=0.5]{figures/ssvi2-y2.eps} &
\includegraphics[scale=0.5]{figures/ssvi2-svi2.eps} \\
\end{tabular}
\label{fig5}
\caption{Predictive distributions of the multioutput gps (left column) and independent gps (right column) for the second toy experiment. The predictive distribution by $g(x)$ for $y_1(x)$ is shown in the bottom figure.}
\end{figure*}

\subsection{EVALUATION OF THE PREDICTIVE ACCURACY}
\subsubsection{Foregin Exchange Rate Prediction}
\subsubsection{Weather Data Prediction}

>>>>

\subsection{TOY PROBLEM}
In this toy problem we use two related outputs generated from the same latent function $sin(x)$ but are corrupted by independent noises: $y_1(x) = sin(x) + \epsilon$ and $y_2(x) = -sin(x) + \epsilon$, $\epsilon \sim \Normal(0,0.01)$.
Each output has missing values in one region of the input space.
% Say that this is from a single gpsvi
The predictive distributions of the model compared to that of independent GPs with stochastic variational inference are shown in figure \ref{fig:toy}.
Furthermore, the inference algorithm correctly learns the correlation between the two functions giving weights $w_{11} = 1.07$ and $w_{21} = -1.06$.

\begin{figure*}
\centering
\begin{tabular}{cccc}
\includegraphics[scale=0.25]{figures/toy-slfm-y1.eps} &
\includegraphics[scale=0.25]{figures/toy-svigp-y1.eps} &
\includegraphics[scale=0.25]{figures/toy-slfm-y2.eps} &
\includegraphics[scale=0.25]{figures/toy-svigp-y2.eps}
\end{tabular}
\caption{Predictive distributions of the multioutput GPs (first and third figure) and independent GPs using stochastic variational inference (second and last figure) for the  toy problem. Solid black line: predictive mean; grey bar: two standard deviations; magenta dots: real observations; blue dots: missing data. The black crosses show the locations of the inducing inputs.}
\label{fig:toy}
\end{figure*}

\subsection{EVALUATION OF THE PREDICTIVE ACCURACY}
\subsubsection{Foregin Exchange Rate Prediction}
In this experiment we predict the foreign exchange rate.
The smse are shown in Table \ref{tab:fx}.

\begin{table}[h]
\caption{Performance comparison by SMSE on the fx dataset.}
\label{tab:fx}
\begin{center}
\begin{tabular}{c|c}
method & smse \\ \hline
SLFM (Q=2) & 0.2232 \\
SLFM (Q=1) & 0.48 \\
CGP & 0.2795 \\
ICM & 0.3927
\end{tabular}
\end{center}
\end{table}

\begin{figure*}
\centering
\begin{tabular}{ccc}
\includegraphics[scale=0.3]{figures/fxAUD.eps} &
\includegraphics[scale=0.3]{figures/fxCAD.eps} &
\includegraphics[scale=0.3]{figures/fxJPY.eps}
\end{tabular}
\caption{Real observations and predictive distributions for AUD (left), CAD (middle), and JPY (right). The color coding scheme is the same as in figure \ref{fig:toy}.}
\label{fig:fx}
\end{figure*}

\subsubsection{Weather Data Prediction}

\begin{figure*}
\centering
\begin{tabular}{cc}
\includegraphics[scale=0.3]{figures/weatherCambermet.eps} &
\includegraphics[scale=0.3]{figures/weatherCambermet.eps} \\
\includegraphics[scale=0.3]{figures/weatherChimet.eps} &
\includegraphics[scale=0.3]{figures/weatherChimet.eps}
\end{tabular}
\caption{Predictive distributions of the multioutput GPs (left column) and full independent GPs (right column) for the air temperature problem.}
\label{fig:toy}
\end{figure*}

### 2014-03-06 paper/inference.tex
add figures and tables

\subsection{Variational Inference}
\newcommand{\ug}{\u_g}
\newcommand{\uh}{\u^h}
\newcommand{\mgj}{\m_j}
\newcommand{\mhi}{\m^h_i}
\newcommand{\Sgj}{\S_j}
\newcommand{\Shi}{\S^h_i}
Our goal of inference is to find the posterior $p(\g, \h, \u, \v | \y)$. 
Following the previous discussion, we assume a variational distribution which factorizes as:
\begin{align}
\nonumber
q(\g, \h, \u, \v | \y)
\nonumber
 &= p(\g|\u) p(\h|\v) q(\u,\v)  \\
 &= p(\g|\u) p(\h|\v) \prod_{j=1}^Q q(\u_j) \prod_{i=1}^P  q(\v_i)
\end{align}
Since the conditionals $p(\g | \u)$ and $p(\h | \v)$ are given, we need only to find the optimum $q(\u_j)$ and $q(\v_i)$.
Let $q(\u_j) = \Normal(\u_j; \mgj, \Sgj)$ and $q(\v_i) = \Normal(\v_i; \mhi, \Shi)$. \\

\noindent
To find the optimum $q(\u, \v)$ we optimize the evidence lower bound (ELBO) of the log marginal,
\begin{align}
\nonumber
\log p(\y) \ge& \int q(\u, \v) \log \frac{p(\y | \u, \v) p(\u, \v)}{q(\u, \v)} \der \u \der \v \\
\nonumber
=& \int q(\u, \v) \log p(\y | \u, \v)  \der \u \der \v 
+ \int q(\u, \v) \log \frac{p(\u, \v)}{q(\u, \v)} \der \u \der \v \\
\label{eq:elbo}
=& \int q(\u, \v) \log p(\y | \u, \v)  \der \u \der \v 
- \left(\sum_{j=1}^Q \KL[q(\u_j) || p(\u_j)] + \sum_{i=1}^P \KL[q(\u_i) || p(\u_i)] \right),
\end{align}
where the last equality occurs because both of $q(\u, \v)$ and $p(\u, \v)$ fully factorize.
Since $q(\u_j), q(\v_i), p(\u_j), p(\v_i)$ are all multivariate Gaussian distributions, the KL divergences are analytically tractable and require $\calO(M^3)$ computation, where $M$ is the largest number of inducing inputs (recall that $g_j(\x)$ and $h_i(\x)$ use separate set of inducing inputs). \\

\noindent To compute the ELBO we first focus on the term:
\newcommand{\llangle}{\left\langle}
\newcommand{\rrangle}{\right\rangle}
\begin{align}
\nonumber
\log p(\y | \u, \v)
 &= \log \Eb{p(\y | \g, \h)}_{p(\g,\h | \u, \v)} \\
 \nonumber
&\ge \Eb{\log p(\y | \g, \h)}_{p(\g,\h | \u, \v)} \quad &\text{(Jensen's inequality)} \\
&= \sum_{i=1}^P \sum_{n=1}^N \Eb{\log p(y_{in} | \g_n, h_{in}) }_{p(\g_n | \u) p(\h_{in} | \v_i)}, \quad 
 &\text{(factorized likelihood)}
\end{align}
where $\g_n = \{g_{jn} = (\g_j)_n\}_{j=1}^Q$.
Each individual term $l_{in} \define \Eb{\log p(y_{in} | \g_n, h_{in}) }_{p(\g_n | \u) p(\h_in | \v_i)}$ can be computed using the identity in eq. \ref{eq:identity} given in the appendix to give:
\begin{align}
\nonumber
l_{in} &= \int \log p(y_{in} | \g_n, h_{in}) \prod_{j=1}^Q p(g_{jn} | \u_j) p(h_{in} | \u_i) \der \g_n \der h_{in} \\
&= \log \Normal(y_{in}; \sum_{j=1}^Q w_{ij} \mu_{jn}+ \mu^h_{in}, \beta_i^{-1})
- \frac{1}{2} \beta_i \sum_{j=1}^Q w_{ij}^2 \tilde{k}_{nn} 
- \frac{1}{2} \beta_i \tilde{k}^h_{inn},
\end{align}
where $\tilde{k}_{nn} = (\tilde{\K})_{nn}, \tilde{k}^h_{inn} = (\tilde{\K}^h_i)_{nn}, \mu_{jn} = (\Mu_j)_n, \text{ and } \mu^h_{in} = (\Mu^h_i)_n$.

% previous detailed derivation
%\begin{align}
%\nonumber
%l_{in} &= \int \log p(y_{in} | g_n, h_{in}) p(\g | \ug) p(\h_i | \u_i) \der \g \der \h_i \\
%\nonumber
%&= \int \log \Normal(y_{in} ; w_i g_n + h_{in}, \beta_i^{-1}) 
%\Normal(g_n ; \mu_{gn}, \tilde{k}_{gnn})
%\Normal(h_{in} ; \mu_{in}, (\tilde{k}_{inn}) \der g_n \der h_{in} \\
%\nonumber
%&= -\frac{1}{2} \log 2 \pi \beta_i^{-1} - \frac{1}{2} \int (y_{in} - w_i g_n - h_{in}) \beta_i (y_{in} - w_i g_n - h_{in})
%\Normal(g_n ; \mu_{gn}, \tilde{k}_{gnn})
%\Normal(h_{in} ; \mu_{in}, \tilde{k}_{inn}) \der g_n \der h_{in} \\
%\nonumber
%&= -\frac{1}{2} \log 2 \pi \beta_i^{-1} - \frac{1}{2} \int \left[(y_{in} - h_{in} - w_i \mu_{gn}) \beta_i (y_{in} - h_{in} - w_i \mu_{gn}) + w_i^2 \beta_i \tilde{k}_{gnn} \right] 
%\Normal(h_{in} ; \mu_{in}, \tilde{k}_{inn}) \der h_{in} \\
%\nonumber
%&= -\frac{1}{2} \log 2 \pi \beta_i^{-1} - \frac{1}{2} w_i^2 \beta_i \tilde{k}_{gnn}
%- \frac{1}{2} \beta_i \tilde{k}_{inn} - \frac{1}{2} (y_{in} - w_i \mu_{gn} - \mu_{in}) \beta_i (y_{in} - w_i \mu_{gn} - \mu_{in}) \\
%&= \log \Normal(y_{in}; w_i \mu_{gn} + \mu_{in}, \beta_i^{-1})  - \frac{1}{2} \beta_i (w_i^2 \tilde{k}_{gnn} + \tilde{k}_{inn}),
%\end{align}

\noindent Substituting $l_{in}$ into equation \ref{eq:elbo} and carrying out the integral using the identity in eq. \ref{eq:identity} we get:
\begin{align}
\nonumber
\log p(\y)
\ge& \sum_{i=1}^P \sum_{n=1}^N
\bigg( \log \Normal(y_{in}; \tilde{\mu}_{in}, \beta_i^{-1})
          - \frac{1}{2} \beta_i \sum_{j=1}^Q w_{ij}^2        \tilde{k}_{nn} - \frac{1}{2} \beta_i \tilde{k}^h_{inn}
 \\ \nonumber
         &\quad \quad \quad \quad - \frac{1}{2} \beta_i \trace  \sum_{j=1}^Q w_{ij}^2 \S_j \mat{\Lambda}_{jn} - \beta_i \frac{1}{2} \trace \S^h_i \mat{\Lambda}_{in} 
\bigg) \\
&- \left(\sum_{j=1}^Q \KL[q(\u_j) || p(\u_j)] + \sum_{i=1}^P \KL[q(\v_i) || p(\v_i)] \right) \define \calL,
\end{align}
where 
%TODO \Lambda_gn depends on the output i so need a better notation
\newcommand{\Zg}{\Z_g}
\newcommand{\Zi}{\Z_i}
\begin{align}
\tilde{\mu}_{in}
&= \sum_{j=1}^Q w_{ij} k(\x_n, \Zj)k(\Zj,\Zj)^{-1}\m_j + k(\x_n, \Zhi)k(\Zhi,\Zhi)^{-1}\mhi \\
\mat{\Lambda}_{jn}
&= k(\Zj,\Zj)^{-1} k(\Zj, \x_n) k(\x_n, \Zj) k(\Zj,\Zj)^{-1} \\
\mat{\Lambda}_{in}
&= k(\Zhi,\Zhi)^{-1} k(\Zhi, \x_n) k(\x_n, \Zhi) k(\Zhi,\Zhi)^{-1}.
\end{align}

\noindent Notice that this ELBO clearly generalizes the standard GP regression. In particular, setting $P = Q = 1$, $w_i = 1$ and $h_i(\x) = 0$ we recover the bound in Hensman et al \cite{hensmangaussian}.
Due to the decomposition of this bound, we can use stochastic gradient descent to learn the variational parameters.

@@

\noindent As a function of the parameters of $q(\u_j)$, the lowerbound $\calL$ is:
\newcommand{\Ahi}{\A^h_i}
\begin{align}
\nonumber
\calL^g_j \define&
 \sum_{i=1}^P \log \Normal(\y_i; \sum_{j=1}^Q w_{ij} \A_j(\oi,:) \m_j + \Ahi \mhi, \beta_i^{-1} \I)  \\
 \nonumber
 &- \frac{1}{2} \sum_{i=1}^P \bigg(\beta_i \trace w_{ij}^2 \tilde{\K}_j(\oi,\oi) 
 + \beta_i \trace w_{ij}^2 \S_j \A_j(\oi,:)^T \A_j(\oi,:) \bigg)
 \\
 &- \frac{1}{2} \log |k(\Zj,\Zj) \S_j^{-1}| -\frac{1}{2} \trace k(\Zj,\Zj)^{-1} (\m_j \m_j^T + \S_j) ,
\end{align}
where $\A_j = k(\X,\Zj)k(\Zj,\Zj)^{-1}$, which gives $\A_j(\oi,:) = k(\X_i,\Zj) k(\Zj,\Zj)^{-1}$, and  
$\Ahi = k(\X_i,\Zhi)k(\Zhi,\Zhi)^{-1}$. \\

%------------------------------------------
% derivatives of q(u_j)
\newcommand{\Lgj}{\calL^g_j}
\newcommand{\ynoj}{\y_i^{\backslash j}}
\noindent The derivatives of $\Lgj$ wrt $\m_j$ and $\S_j$ are given by:
\begin{align}
\deriv{\Lgj}{\m_j}
& = \sum_{i=1}^P \beta_i w_{ij} \A_j(\oi,:)^T \ynoj - \bigg[k_g(\Zg,\Zg)^{-1} + \sum_{i=1}^P \beta_i w_{ij}^2 \A_j(\oi,:)^T \A_j(\oi,:) \bigg] \m_j \\
\deriv{\Lgj}{\S_j} 
&= \frac{1}{2} \S_j^{-1} - \frac{1}{2} \bigg[ k(\Zj,\Zj)^{-1} + \sum_{i=1}^P \beta_i w_{ij}^2 \A_j(\oi,:)^T \A_j(\oi,:) \bigg],
\end{align}
where $\y_i^{\backslash j} = \y_i - \Ahi \mhi - \sum_{j' \neq j} w_{ij'} \A_{j'}(\oi,:) \m_{j'}$.

%-------------------------------------------
%  derivatives of q(v_i)
\newcommand{\Lhi}{\calL^h_i}
\noindent As a function of the parameters of $q(\v_i)$, the lower bound $\calL$ is:
\begin{align}
\nonumber
\Lhi \define&
 \log \Normal(\y_i; \sum_{j=1}^Q w_{ij} \A_j(\oi,:) \m_j + \Ahi \mhi, \beta_i^{-1} \I)
 - \frac{1}{2} \beta_i \trace \tilde{\K}^h_i(\oi,\oi)
 - \frac{1}{2} \beta_i \trace \Shi (\Ahi)^T \Ahi
 \\
  &- \frac{1}{2} \log |k(\Zhi,\Zhi) (\Shi)^{-1}| -\frac{1}{2} \trace k(\Zhi,\Zhi)^{-1} (\mhi (\mhi)^T + \Shi) ,
\end{align}

\noindent The derivatives of $\Lhi$ wrt $\mhi$ and $\Shi$ are given by:
\newcommand{\ynoh}{\y_i^{\backslash h}}
\begin{align}
\deriv{\Lhi}{\mhi}
& = \beta_i \A_i^T \ynoh - \left[k(\Zhi,\Zhi)^{-1} +  \beta_i \A_i^T \A_i \right] \m_i \\
\deriv{\Lhi}{\Shi} 
&= \frac{1}{2} \S_i^{-1} - \frac{1}{2} \left[ k(\Zhi,\Zhi)^{-1} + \beta_i \A_i^T \A_i \right] ,
\end{align}
where $\ynoh = \y_i - \sum_{j=1}^Q w_{ij} \A_j(\oi,:) \m_j$.

>>>>

\subsection{Variational Inference}
\newcommand{\ug}{\u_g}
\newcommand{\uh}{\u^h}
\newcommand{\mgj}{\m_j}
\newcommand{\mhi}{\m^h_i}
\newcommand{\Sgj}{\S_j}
\newcommand{\Shi}{\S^h_i}
Our goal of inference is to find the posterior $p(\g, \h, \u, \v | \y)$. 
Following the previous discussion, we assume a variational distribution which factorizes as:
\begin{align}
\nonumber
q(\g, \h, \u, \v | \y)
\nonumber
 &= p(\g|\u) p(\h|\v) q(\u,\v)  \\
 &= p(\g|\u) p(\h|\v) \prod_{j=1}^Q q(\u_j) \prod_{i=1}^P  q(\v_i)
\end{align}
Since the conditionals $p(\g | \u)$ and $p(\h | \v)$ are given, we need only  find the optimum $q(\u_j) = \Normal(\u_j; \mgj, \Sgj)$ and $q(\v_i) = q(\v_i) = \Normal(\v_i; \mhi, \Shi)$.

\noindent
In variational inference, this is done by optimizing the evidence lower bound (ELBO) of the log marginal:
\begin{align}
%\nonumber
%\log p(\y) \ge& \int q(\u, \v) \log \frac{p(\y | \u, \v) p(\u, \v)}{q(\u, \v)} \der \u \der \v \\
%\nonumber
%=& \int q(\u, \v) \log p(\y | \u, \v)  \der \u \der \v 
%+ \int q(\u, \v) \log \frac{p(\u, \v)}{q(\u, \v)} \der \u \der \v \\
\nonumber
&\log p(\y) \ge \int q(\u, \v) \log p(\y | \u, \v)  \der \u \der \v \\
&- \sum_{j=1}^Q \KL[q(\u_j) || p(\u_j)] - \sum_{i=1}^P \KL[q(\u_i) || p(\u_i)],
\label{eq:elbo}
\end{align}
which is derived using Jensen's inequality and the fact that both of $q(\u, \v)$ and $p(\u, \v)$ fully factorize.
Since $q(\u_j), q(\v_i), p(\u_j), p(\v_i)$ are all multivariate Gaussian distributions, the KL divergences are analytically tractable and require $\calO(M^3)$ computation. To compute the expected likelihood term in the ELBO we first see that
\begin{align}
\nonumber
\log \text{ } &p(\y | \u, \v)
% &= \log \Eb{p(\y | \g, \h)}_{p(\g,\h | \u, \v)} \\
% \nonumber
\ge \Eb{\log p(\y | \g, \h)}_{p(\g,\h | \u, \v)}  \\
&= \sum_{i=1}^P \sum_{n=1}^N \Eb{\log p(y_{in} | \g_n, h_{in}) }_{p(\g_n | \u) p(\h_{in} | \v_i)} 
\end{align}
where $\g_n = \{g_{jn} = (\g_j)_n\}_{j=1}^Q$.
The inequality is due to Jensen's inequality and the equality is due to the fact that the likelihood fully factorizes.
Each individual term $l_{in} \define \Eb{\log p(y_{in} | \g_n, h_{in}) }_{p(\g_n | \u) p(\h_in | \v_i)}$ is computed using the identity in eq. \ref{eq:identity} and  given in eq \ref{eq:lin} (both are in the Appendix).
\newcommand{\Ahi}{\A^h_i}
\newcommand{\Zi}{\Z_i}
 Substituting $l_{in}$ into equation \ref{eq:elbo} and carrying out the integral using the identity in eq. \ref{eq:identity} again we get:
\begin{align}
\nonumber
&\log p(\y)
\ge \sum_{i,n}
\bigg( \log  \Normal(y_{in}; \tilde{\mu}_{in}, \beta_i^{-1})
          - \frac{1}{2} \beta_i \sum_{j=1}^Q w_{ij}^2 \tilde{k}_{nn} \\ \nonumber
         &- \frac{1}{2} \beta_i \tilde{k}^h_{inn}
         - \frac{1}{2} \beta_i \trace  \sum_{j=1}^Q w_{ij}^2 \S_j \mat{\Lambda}_{jn} - \beta_i \frac{1}{2} \trace \S^h_i \mat{\Lambda}_{in} 
\bigg) \\
&- \sum_{j=1}^Q \KL[q(\u_j) || p(\u_j)] - \sum_{i=1}^P \KL[q(\v_i) || p(\v_i)]  \define \calL,
\end{align}
where, with the help of the auxiliary matrices $\A_j = k(\X,\Zj)k(\Zj,\Zj)^{-1}$ and  
$\Ahi = k(\X_i,\Zhi)k(\Zhi,\Zhi)^{-1}$, 
\begin{align}
\tilde{\mu}_{in}
%&= \sum_{j=1}^Q w_{ij} k(\x_n, \Zj)k(\Zj,\Zj)^{-1}\m_j + k(\x_n, \Zhi)k(\Zhi,\Zhi)^{-1}\mhi \\
&= \sum_{j=1}^Q w_{ij} \A_j(n,:) \m_j + \Ahi(n,:) \mhi \\
\mat{\Lambda}_{jn}
%&= k(\Zj,\Zj)^{-1} k(\Zj, \x_n) k(\x_n, \Zj) k(\Zj,\Zj)^{-1} \\
&= \A_j(n,:)^T \A_j(n,:)  \\
\mat{\Lambda}_{in}
%&= k(\Zhi,\Zhi)^{-1} k(\Zhi, \x_n) k(\x_n, \Zhi) k(\Zhi,\Zhi)^{-1}
&= \Ahi(n,:)^T \Ahi(n,:) 
\end{align}
where $\tilde{k}_{nn} = (\tilde{\K})_{nn}$, $\tilde{k}^h_{inn} = (\tilde{\K}^h_i)_{nn}$, $\mu_{jn} = (\Mu_j)_n$,  $\mu^h_{in} = (\Mu^h_i)_n$, and $\A_j(n,:)$ selects the $n$-th row vector of $\A_j$.

% More on this elbo term
\noindent Notice that this ELBO clearly generalizes the standard GP regression. In particular, setting $P = Q = 1$, $w_i = 1$ and $h_i(\x) = 0$ we recover the bound in Hensman et al \cite{hensmangaussian}.
Due to the decomposition of this bound, we can use stochastic gradient descent to learn the variational parameters.

@@

%\noindent As a function of the parameters of $q(\u_j)$, the lowerbound $\calL$ is:
%\begin{align}
%\nonumber
%\calL^g_j \define&
% \sum_{i=1}^P \log \Normal(\y_i; \sum_{j=1}^Q w_{ij} \A_j(\oi,:) \m_j + \Ahi \mhi, \beta_i^{-1} \I)  \\
% \nonumber
% &- \frac{1}{2} \sum_{i=1}^P \bigg(\beta_i \trace w_{ij}^2 \tilde{\K}_j(\oi,\oi) 
% + \beta_i \trace w_{ij}^2 \S_j \A_j(\oi,:)^T \A_j(\oi,:) \bigg)
% \\
% &- \frac{1}{2} \log |k(\Zj,\Zj) \S_j^{-1}| -\frac{1}{2} \trace k(\Zj,\Zj)^{-1} (\m_j \m_j^T + \S_j) ,
%\end{align}
%where $\A_j = k(\X,\Zj)k(\Zj,\Zj)^{-1}$, which gives $\A_j(\oi,:) = k(\X_i,\Zj) k(\Zj,\Zj)^{-1}$, and  
%$\Ahi = k(\X_i,\Zhi)k(\Zhi,\Zhi)^{-1}$. \\

%------------------------------------------
% derivatives of q(u_j)
\newcommand{\Lgj}{\calL^g_j}
\newcommand{\ynoj}{\y_i^{\backslash j}}
\newcommand{\Kjzz}{\mat{K}_{jzz}}
\noindent The derivatives of $\calL$ wrt $\m_j$ and $\S_j$ are given by:
\begin{align}
\nonumber
\deriv{\calL}{\m_j} 
=& \sum_{i=1}^P \beta_i w_{ij} \A_j(\oi,:)^T \ynoj \\
&- \bigg[\Kjzz^{-1} + \sum_{i=1}^P \beta_i w_{ij}^2 \A_j(\oi,:)^T \A_j(\oi,:) \bigg] \m_j \\
\deriv{\calL}{\S_j} 
=& \frac{1}{2} \S_j^{-1} - \frac{1}{2} \bigg[ \Kjzz^{-1} + \sum_{i=1}^P \beta_i w_{ij}^2 \A_j(\oi,:)^T \A_j(\oi,:) \bigg],
\end{align}
where $\Kjzz = k(\Zj,\Zj)$ and $\y_i^{\backslash j} = \y_i - \Ahi(\oi,:) \mhi - \sum_{j' \neq j} w_{ij'} \A_{j'}(\oi,:) \m_{j'}$.

%-------------------------------------------
%  derivatives of q(v_i)
%\noindent As a function of the parameters of $q(\v_i)$, the lower bound $\calL$ is:
%\begin{align}
%\nonumber
%\Lhi \define&
% \log \Normal(\y_i; \sum_{j=1}^Q w_{ij} \A_j(\oi,:) \m_j + \Ahi \mhi, \beta_i^{-1} \I)
% - \frac{1}{2} \beta_i \trace \tilde{\K}^h_i(\oi,\oi)
% - \frac{1}{2} \beta_i \trace \Shi (\Ahi)^T \Ahi
% \\
%  &- \frac{1}{2} \log |k(\Zhi,\Zhi) (\Shi)^{-1}| -\frac{1}{2} \trace k(\Zhi,\Zhi)^{-1} (\mhi (\mhi)^T + \Shi) ,
%\end{align}
\newcommand{\Lhi}{\calL^h_i}
\newcommand{\Kizz}{\mat{K}_{izz}}
\noindent The derivatives of $\calL$ wrt $\mhi$ and $\Shi$ are given by:
\newcommand{\ynoh}{\y_i^{\backslash h}}
\begin{align}
\nonumber
\deriv{\calL}{\mhi}
= & \beta_i (\Ahi(\oi,:))^T \ynoh \\ 
& - \bigg[\Kizz^{-1} +  \beta_i (\Ahi(\oi,:))^T \Ahi(\oi,:) \bigg] \m_i \\
\deriv{\calL}{\Shi} 
&= \frac{1}{2} \S_i^{-1} - \frac{1}{2} \bigg[ \Kizz^{-1} + \beta_i \Ahi(\oi,:))^T \Ahi(\oi,:) \bigg] ,
\end{align}
where $\ynoh = \y_i - \sum_{j=1}^Q w_{ij} \A_j(\oi,:) \m_j$ and $\Kizz = k(\Zhi, \Zhi)$.
